\section{Differential Equations}\label{sec-diff-eq}

There are several types of differential equations that we are successively going
to study in the sub-sections to come. An \gls{ode} is a linear or nonlinear
differential equation with one independent variable, while a \gls{pde} has at least
two independent variables which can also be further divided into linear and nonlinear
differential equations. In addition to all of that, differential equations are
further described by their order that is determined by the term with the highest
derivatives, or whether they are said to be homogeneous or heterogenous. It is
important to understand these concepts because they are useful to remember which
approach to take in order to find an analytical solution. Unfortunately, we will
encounter many differential equations that are either very hard or impossible to
solve without numerical methods. Even so there are many good reasons to dedicate
a good amount of time to studying differential equations: their usefulness
comes into play whenever it is easier to describe change than absolute amounts.
They are omnipresent in the natural sciences capable of describing the laws of
nature in a way that is very succinct yet non-trivial, as there is often more to
them than one would suspect at first glance. Appreciation for their beauty may
grow much more pronounced once we take a look into a more generalized theory of
differential equations. However, this endeavor requires some hands-on experience
in order to build up the necessary intuition to progress this path.
